Geometric variational problems

### 2020-11-16 NSF2020/Description/specificaim1_ver2.tex
done aim 1

Hamm and Kozlov (HK) pioneered 
the modern theory of membrane continuum mechanics \cite{Hamm2000}, and their theory
%was pioneered by Hamm and Kozlov (HK) \cite{Hamm2000}. The theory 
is widely used to describe biological phenomena, including 
fission \cite{FrEsAkSh15, Maetal15, PhysRevE.79.031926},
fusion \cite{ChKo08, KoKo2002,Kuzmin7235,Aeffner2012},
poration \cite{Gaetal20}, phase boundaries, and interaction with inclusions
\cite{SeLeMaEg17,Saetal20, Pietal20}. These phenomena
require resolution of the internal structure of the membrane.  
Recently, there has been a revival in interest in the HK theory as the quadratic assumption
for the elasticity energy density has caused
researchers to question the applicability of the theory 
for large curvatures
\cite{PhysRevLett.117.188102, ARGUDO20161619}.
%
\begin{wrapfigure}[11]{l}{0.47\textwidth}
\centerline{\includegraphics[width=0.47\textwidth]{Figures/Deformations.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
  \vspace{-5pt}
\caption{\label{fig:deformations} \footnotesize Sketch of the HK
 membrane model \cite{Hamm2000}.}
\end{wrapfigure}
%
This proposal will develop much-needed mathematical analysis to resolve
these controversies due to the assumptions in the HK theory. 
%Using the HK  model as a base,
%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.

@@

Although the HK elastic theory assumes small deformations, 
Galimzyanov {\em et al.}~\cite{C9SM02079A} have shown that energies derived from
molecular dynamics and those derived from \eqref{ansatz3} are in agreement, even when curvatures are large.
Under spatial scales much larger than the
membrane thickness, membrane energy is well-characterized by the
Canham-Helfrich energy used throughout the fluid-structure literature
\cite{QiangDu09, Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP, qua-bir2014, qua-vee-you2019}.
%\todo[inline]{YNY: place your recent works here}
The Canham-Helfrich energy is actually a special case of
\eqref{ansatz3} obtained by setting ${\bf n} =  \pm {\bf N}$ (the $\pm$ depending on
orientation) and collapsing both monolayers onto the membrane midplane.
%There, splay $\Div n$ equal to twice the mean curvature, saddle splay
%$\det \nabla n$ equal to the Gauss curvature, and both twist and tilt
%are equal to zero.

@@

%\begin{center}
%Anticipated model simulations
%\end{center}
\newpage
\subsubsection{Simulations of the HAP model to estimate elastic moduli
and energy}
%To characterize material properties of a bilayer, we compare the energies and forces generated by
%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
%
%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
%for a wide range of particle parameters and physical parameters in HARP to 
%
%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
%as the corresponding energies in the particle system for all reasonable deformation.
%If this is the case we will 
%
\begin{wrapfigure}[10]{r}{0.4\textwidth}
\vspace{-0.3cm}
\centerline{\includegraphics[width=0.4\textwidth]{Figures/Flattening.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
\vspace{-0.2cm}
\caption{\label{fig:flattening} \footnotesize Example of computing
  bending modulus of a lipid bilayer from particle simulation.}
\end{wrapfigure}
We propose to {\bf (i)} determine the value of effective elastic moduli $\KB$,
$\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and
particle shape map onto elastic moduli. 
An accurate and robust way to measure material properties is to track the evolution of the bilayer as
it relaxes from an initially non-equilibrium
configuration~\cite{PhysRevLett.117.188102}. Figure~\ref{fig:flattening}
shows an example where the initial configuration of a bilayer
patch containing the splay deformation without any other components
(saddle splay, twist and tilt). As the bent membrane flattens, 
both the self-interaction energy $\Phi$ and the elastic
energy ${\cal W}$ decrease, and because the saddle splay, twist, and
tilt stay zero, the slope gives the bending modulus in this case.

@@

Here we start with a particle-based bilayer in a specific non-equilibrium shape that involves only one of the components of the displacement in Figure~\ref{fig:deformations}, and then evolve the particle system according to the time integration for \eqref{eq:stokes}.
Because elastic properties are independent of dissipation,
we can forgo solving for fluid velocity and set the translational
velocity and angular velocity directly proportional to force and torque. 
%bilayer by steepest gradient descent 
%with respect to the HARP functional:
%\begin{equation}
%\label{SGD}   
%\frac{\dif {\bf a}_i}{\dif t} = {\bf F}_i,    \quad  \frac{\dif {\bf R}_i}{\dif t}  = {\bf R}_i A({\bf w}_i),\quad i = 1, \dots, N.
%\end{equation}
%where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; %
%$A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
%We solve \eqref{SGD} numerically  using an Adams–Bashforth linear multistep method. 
%The procedure involves solving \eqref{SL} based off of the current particle configuration.
%We then use the solution $u$ to calculate the collection of forces and torques \eqref{forceandtorque}, and update the particle configuration
%through \eqref{SGD}.
%
This yields a dissipation of the total potential \eqref{eq:total_poten}, which
stabilizes the evolving bilayer shape.
Therefore, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field ${\bf n}$ by
interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$ from the interpolated shapes.

@@

\noindent{\bf{HK elastic energy form:}}
The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
\textbf{(i)} Researchers have assumed that $\KT = 0$ to effect lateral fluidity in
membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
PhysRevE.102.042406}. 
A value $\KT = 0$, however, makes \eqref{ansatz3} a noncoercive functional.
%and leads to the nonphysical conclusion that there are bilayers 
%with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
\textbf{(ii)} Recently,~\cite{TerziDeserno17} derived a tilt curvature
term that was neglected from the HK analysis~\cite{Hamm2000}.
Later,~\cite{C9SM02079A} and~\cite{PhysRevE.102.042406} independently
identified an inconsistency in the argument used
by~\cite{TerziDeserno17} arising
from a transversal tilt invariance assumption.
In~\cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
\textbf{(iii)} Theoretical analysis of lipid phase transitions predict a
negative saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
SIEGEL20085200} that gives rise to a larger energy barrier for
monolayer fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
TerziDeserno17}.
%
%
%Researchers point out, however, that this theoretical value requires a larger energy 
%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
%Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.

@@

%  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
%  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
%  and accounting for these couplings by Taylor expansion  
%  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
%
%The form of the elastic energy density \eqref{ansatz3} is the same as
%  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
%  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
%  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
%  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
%  Using this observation, we prove an exact identity 
%  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
%  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
%  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
%  
%%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
%%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
%%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
%%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
%%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
%%  This gives the continuum elastic energy equals
%%  \begin{equation}
%%    \label{eq:twist_energy}
%%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
%%  \end{equation}
%%  which we compare to the HAP simulation data.
%
\subsubsection{Analysis on the HAP model in terms of the HK functional}
The HK functional \eqref{ansatz3} has had tremendous impact in understanding
biological membranes, but has received little attention in terms of mathematical
analysis. In the calculus of variations, the principal question is whether a
minimizer of an energy functional exists. But in the case of \eqref{ansatz3},
this answer is presently unknown. With regard to the simpler, Canham-Helfrich
energy, \cite{Simon1993} proved the existence of minimizing surfaces without boundary, 
and \cite{doi:10.1137/18M1195851} proved the well-posedness of a spatially periodic,
time-dependent elastic interface problem. An analytical challenge 
for the HK functional \eqref{ansatz3} is that surface-director coupling makes it
possible to have bounded energy monolayers with corners, and such
pathological examples must be ruled out before carrying over the arguments
for the Canham-Helfrich functional to the present setting.

%\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
Our goal here is to develop tools that can explain functionals like
\eqref{ansatz3} from first principles in terms of HAP. The papers
\cite{doi:10.1063/5.0009734,Seguin2012,Seguin2014} give statistical
mechanical/mean field derivations of the Canham-Helfrich energy from a
pair-potential for rod-like molecules, but do not include tilt, which is an
indispensable deformation at biological scales. To make progress, we must
first understand how the HAP functional behaves under various limits.

We first consider HAP in the limit of vanishing screening length.
As a concrete, model problem we consider a collection of colloidal polyhedral
where the binding energy of this system can be described by a
discrete, lower semicontinuous functional $\Phi_0$ whose value is the total
surface area of the polyhedra minus two times the area of any overlapping faces.
We conjecture that the $\Phi$ energy $\Gamma$-converges to $\Phi_0$
\cite{Mugnai2013}, meaning that any cluster points of minimizers of $\Phi$
converge to a minimum of $\Phi_0$ in the limit $\rho \to 0$. 
To address this conjecture, we employ boundary layer analysis for the screened
Laplace equation \cite{Lee2018, Lin2015, Shibata2004,1531-3492_2006_2_357, Lee2018}.
The technique of $\Gamma$-convergence is a powerful tool for numerical approximations
and with it we can help explain unexcepted phenomena like hierarchical self-assembly in
colloidal systems \cite{Luo2019}.

>>>>

Hamm and Kozlov (HK) pioneered the modern theory of membrane continuum
mechanics~\cite{Hamm2000}, and their theory is widely used to describe
biological phenomena, including fission \cite{FrEsAkSh15, Maetal15,
PhysRevE.79.031926}, fusion \cite{ChKo08,
KoKo2002,Kuzmin7235,Aeffner2012}, poration~\cite{Gaetal20}, phase
boundaries, and interaction with inclusions~\cite{SeLeMaEg17,Saetal20,
Pietal20}. These phenomena require resolution of the internal structure
of the membrane.  Recently, there has been a revival of interest in the
HK theory as the quadratic assumption for the elasticity energy density
has caused researchers to question the applicability of the theory for
large curvatures~\cite{PhysRevLett.117.188102, ARGUDO20161619}.
%
\begin{wrapfigure}[11]{l}{0.47\textwidth}
\centerline{\includegraphics[width=0.47\textwidth]{Figures/Deformations.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
  \vspace{-5pt}
\caption{\label{fig:deformations} \footnotesize Sketch of the HK
 membrane model \cite{Hamm2000}.}
\end{wrapfigure}
%
This proposal will develop much-needed mathematical analysis to resolve
these controversies due to the assumptions in the HK theory. 
%Using the HK  model as a base,
%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.

@@

Although the HK elastic theory assumes small deformations, 
Galimzyanov {\em et al.}~\cite{C9SM02079A} have shown that energies derived from
molecular dynamics and those derived from \eqref{ansatz3} are in agreement, even when curvatures are large.
Under spatial scales much larger than the membrane thickness, membrane
energy is well-characterized by the Canham-Helfrich energy used
throughout the fluid-structure literature \cite{QiangDu09,
Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP, qua-bir2014,
qua-vee-you2019}. The Canham-Helfrich energy is actually a special case
of \eqref{ansatz3} obtained by setting ${\bf n} =  \pm {\bf N}$ (the
$\pm$ depending on orientation) and collapsing both monolayers onto the
membrane midplane.
%There, splay $\Div n$ equal to twice the mean curvature, saddle splay
%$\det \nabla n$ equal to the Gauss curvature, and both twist and tilt
%are equal to zero.

@@

%\begin{center}
%Anticipated model simulations
%\end{center}
\newpage
\subsubsection{Simulations of the HAP model to estimate elastic moduli
and energy}
%To characterize material properties of a bilayer, we compare the energies and forces generated by
%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
%
%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
%for a wide range of particle parameters and physical parameters in HARP to 
%
%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
%as the corresponding energies in the particle system for all reasonable deformation.
%If this is the case we will 
%
\begin{wrapfigure}[9]{r}{0.43\textwidth}
\vspace{-0.4cm}
\centerline{\includegraphics[width=0.43\textwidth]{Figures/Flattening.pdf}}
%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
\vspace{-0.5cm}
\caption{\label{fig:flattening} \footnotesize Example of computing
  bending modulus of a lipid bilayer from particle simulation.}
\end{wrapfigure}
We propose to {\bf (i)} determine the value of effective elastic moduli
$\KB$, $\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the
model parameters $\rho,$ $\gamma$, and the particle shape map onto
elastic moduli. An accurate and robust way to measure material
properties is to track the evolution of the bilayer as it relaxes from
an initially non-equilibrium
configuration~\cite{PhysRevLett.117.188102}.
Figure~\ref{fig:flattening} shows an example where the initial
configuration of a bilayer patch containing the splay deformation
without any other components (saddle splay, twist and tilt). As the bent
membrane flattens, both the self-interaction energy $\Phi$ and the
elastic energy ${\cal W}$ decrease, and because the saddle splay, twist,
and tilt stay zero, the slope gives the bending modulus in this case.

@@

Here we start with a particle-based bilayer in a specific
non-equilibrium shape that involves only one of the components of the
displacement in Figure~\ref{fig:deformations}, and then evolve the
particle system according to the time integration for \eqref{eq:stokes}.
Because elastic properties are independent of dissipation, we can forgo
solving for fluid velocity and set the translational velocity and
angular velocity directly proportional to the force and torque,
respectively. 
%bilayer by steepest gradient descent 
%with respect to the HARP functional:
%\begin{equation}
%\label{SGD}   
%\frac{\dif {\bf a}_i}{\dif t} = {\bf F}_i,    \quad  \frac{\dif {\bf R}_i}{\dif t}  = {\bf R}_i A({\bf w}_i),\quad i = 1, \dots, N.
%\end{equation}
%where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; %
%$A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
%We solve \eqref{SGD} numerically  using an Adams–Bashforth linear multistep method. 
%The procedure involves solving \eqref{SL} based off of the current particle configuration.
%We then use the solution $u$ to calculate the collection of forces and torques \eqref{forceandtorque}, and update the particle configuration
%through \eqref{SGD}.
%
This yields a dissipation of the total potential \eqref{eq:total_poten}, which
stabilizes the evolving bilayer shape.
Therefore, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field ${\bf n}$ by
interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$ from the interpolated shapes.

@@

\noindent{\bf{HK elastic energy form:}}
The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
\textbf{(i)} Researchers have assumed that $\KT = 0$ to effect lateral fluidity in
membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
PhysRevE.102.042406}. 
A value $\KT = 0$, however, makes~\eqref{ansatz3} a noncoercive functional.
%and leads to the nonphysical conclusion that there are bilayers 
%with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
\textbf{(ii)} Recently,~\cite{TerziDeserno17} derived a tilt curvature
term that was neglected from the HK analysis~\cite{Hamm2000}.
Later,~\cite{C9SM02079A} and~\cite{PhysRevE.102.042406} independently
identified an inconsistency in the argument used
by~\cite{TerziDeserno17} arising
from a transversal tilt invariance assumption.
In~\cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
\textbf{(iii)} Theoretical analysis of lipid phase transitions predict a
negative saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
SIEGEL20085200} that gives rise to a larger energy barrier for
monolayer fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
TerziDeserno17}.
%
%
%Researchers point out, however, that this theoretical value requires a larger energy 
%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
%Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.

@@

%  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
%  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
%  and accounting for these couplings by Taylor expansion  
%  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
%
%The form of the elastic energy density \eqref{ansatz3} is the same as
%  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
%  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
%  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
%  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
%  Using this observation, we prove an exact identity 
%  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
%  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
%  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
%  
%%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
%%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
%%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
%%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
%%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
%%  This gives the continuum elastic energy equals
%%  \begin{equation}
%%    \label{eq:twist_energy}
%%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
%%  \end{equation}
%%  which we compare to the HAP simulation data.
%
\subsubsection{Analysis on the HAP model in terms of the HK functional}
The HK functional~\eqref{ansatz3} has had tremendous impact in
understanding biological membranes, but has received little attention in
terms of mathematical analysis. In the calculus of variations, the
principal question is whether a minimizer of an energy functional
exists. In the case of~\eqref{ansatz3}, the answer is presently unknown.
With regard to the simpler Canham-Helfrich energy,~\cite{Simon1993}
proved the existence of minimizing surfaces without boundary,
and~\cite{doi:10.1137/18M1195851} proved the well-posedness of a
spatially periodic, time-dependent elastic interface problem. An
analytical challenge for the HK functional~\eqref{ansatz3} is that
surface-director coupling makes it possible to have bounded energy
monolayers with corners, and such pathological examples must be ruled
out before carrying over the arguments for the Canham-Helfrich
functional to the present setting.

%\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of
%HAP}
Our goal here is to develop tools that can explain functionals
like~\eqref{ansatz3} from first principles in terms of HAP. The
papers~\cite{doi:10.1063/5.0009734, Seguin2012, Seguin2014} give
statistical mechanical/mean field derivations of the Canham-Helfrich
energy from a pair-potential for rod-like molecules, but do not include
tilt, which is an indispensable deformation at biological scales. To
make progress, we must first understand how the HAP functional behaves
under various limits.

We first consider HAP in the limit of vanishing screening length. As a
concrete model problem, we consider a collection of colloidal polyhedral
where the binding energy of this system can be described by a discrete,
lower semicontinuous functional $\Phi_0$ whose value is the total
surface area of the polyhedra minus two times the area of any
overlapping faces. We conjecture that the $\Phi$ energy
$\Gamma$-converges to $\Phi_0$ \cite{Mugnai2013}, meaning that any
cluster points of minimizers of $\Phi$ converge to a minimum of $\Phi_0$
in the limit $\rho \to 0$. To address this conjecture, we employ
boundary layer analysis for the screened Laplace equation~\cite{Lee2018,
Lin2015, Shibata2004,1531-3492_2006_2_357, Lee2018}. The technique of
$\Gamma$-convergence is a powerful tool for numerical approximations and
with it we can help explain unexpected phenomena like hierarchical
self-assembly in colloidal systems~\cite{Luo2019}.
